### 2019-05-08 papers/haskell19/6-casestudies.tex
Minor changes, fixed layout, added citation

\begin{figure}[t]
  \centering
  \begin{tikzpicture}
    \begin{axis}
      [ height=4.5cm
      , width=9cm
      , ybar
      , ymajorgrids=true
      , ytick={0,1,...,4}
      , ymax=3.7
      , ymin=0.7
      , enlargelimits=0.3
      , enlarge x limits=0.25
      , /pgf/bar width=17pt
      , legend style={
        at={(0.5,-0.2)},
        anchor=north,legend columns=3}
      , legend image code/.code={%
        \draw[#1, draw=none] (0cm,-0.1cm) rectangle (0.3cm,0.2cm); }
      , ylabel={Relative Generation Time}
      , symbolic x coords={RBT, SExp, HTML}
      , xtick=data
      % , nodes near coords
      , nodes near coords align={vertical}
      ]
      \addplot[fill, red!30]   coordinates {(SExp,1)    (RBT,1)    (HTML,1)};
      \addplot[fill, green!30] coordinates {(SExp,2.40) (RBT,3.57) (HTML,4.27)};
      \addplot[fill, blue!30]  coordinates {(SExp,1.60) (RBT,2.52) (HTML,1.55)};
      \legend{Manual, Modular (lin), Modular (bal)}
    \end{axis}
  \end{tikzpicture}
  \vspace{-7pt}
  \caption{Generation time comparison between concrete and modular generators.}
  \label{fig:times}
  \vspace{-18pt}
\end{figure}

>>>>

\begin{figure}[b]
  \vspace{-10pt}
  \centering
  \begin{tikzpicture}
    \begin{axis}
      [ height=5cm
      , width=9cm
      , ybar
      , ymajorgrids=true
      , ytick={0,1,...,4}
      , ymax=3.7
      , ymin=0.7
      , enlargelimits=0.3
      , enlarge x limits=0.25
      , /pgf/bar width=17pt
      , legend style={
        at={(0.5,-0.25)},
        anchor=north,legend columns=3}
      , legend image code/.code={%
        \draw[#1, draw=none] (0cm,-0.1cm) rectangle (0.3cm,0.2cm); }
      , ylabel={Relative Generation Time}
      , symbolic x coords={RBT, SExp, HTML}
      , xtick=data
      % , nodes near coords
      , nodes near coords align={vertical}
      ]
      \addplot[fill, red!30]   coordinates {(SExp,1)    (RBT,1)    (HTML,1)};
      \addplot[fill, green!30] coordinates {(SExp,2.40) (RBT,3.57) (HTML,4.27)};
      \addplot[fill, blue!30]  coordinates {(SExp,1.60) (RBT,2.52) (HTML,1.55)};
      \legend{Manual, Modular (lin), Modular (bal)}
    \end{axis}
  \end{tikzpicture}
  \vspace{-7pt}
  \caption{Generation time comparison between concrete and modular generators.}
  \label{fig:times}
  \vspace{-5pt}
\end{figure}

### 2019-05-08 papers/haskell19/7-related.tex
Minor changes, fixed layout, added citation

In the past few years, there has been a bloom of derivation tools for
synthesizing random generators.
%
\emph{Feat} provides a mechanism to uniformly generating values from a given
data type \cite{DuregardJW12}.
%
It works by enumerating all the possible values of such type, so that sampling
uniformly from it simply becomes sampling uniformly from the a finite prefix of
natural numbers---something easy to do.

\emph{MegaDeTH} is a simple derivation tool that derives generators solely based
on their types, paying no attention whatsoever to the generation frequency of
each data constructor.
%
As a result, its automatically derived generators has been shown to be skewed
towards generating very small values
\cite{DBLP:conf/haskell/MistaRH18}.\looseness=-1

>>>>

In the past few years, there has been a bloom of derivation tools for
synthesizing random generators.
%
\emph{Feat} provides a mechanism to uniformly generating values from a given
data type \cite{DuregardJW12}.
%
It works by enumerating all the possible values of such type, so that sampling
uniformly from it simply becomes sampling uniformly from a finite prefix of
natural numbers---something easy to do.

\emph{MegaDeTH} is a simple derivation tool that synthesizes generators solely
based on their types, paying no attention whatsoever to the generation frequency
of each data constructor.
%
As a result, its automatically derived generators has been shown to be skewed
towards generating very small values
\cite{DBLP:conf/haskell/MistaRH18}.\looseness=-1

### 2019-05-08 papers/haskell19/abstract.tex
Minor changes, fixed layout, added citation

In this work, we develop an extensible framework for deriving compositional
generators, which can be easily combined in different ways in order to fit the
developers' demands, using a simple type-level description language.
%
Our framework relies on familiar ideas from the \`a la Carte technique for
writing composable interpreters in Haskell.
%
In this light, we adapt this technique with the machinery required in the scope
of random generation.
%
We provide an implementation of our ideas, and evaluate its performance using
real-world examples.
%

>>>>

In this work, we develop an extensible framework for deriving compositional
generators, which can be easily combined in different ways in order to fit the
developers' demands using a simple type-level description language.
%
Our framework relies on familiar ideas from the \`a la Carte technique for
writing composable interpreters in Haskell.
%
In particular, we adapt this technique with the machinery required in the scope
of random generation.
%
We provide an implementation of our ideas, and evaluate its performance using
real-world examples.
%
